---
title: "Shiny_presentation"
author: "Bryent Lee"
date: "7/2/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Data Summary Table

- Uses data from Rstudio buildin datasets 
- Cars, Rock, Pressure, US Arrests
- Immediately get the summary table and head of each data sets depending on the input
- Total Observations are also printed

## Link to app
- To use app, click [here](https://blee408.shinyapps.io/first_app/)
- To gain access for [github files for ui.R, server.R, Presentation R markdown](https://github.com/bryentlee/first-)
- Summary table contained mean, median, 1 & 3 quantile, minimum and maximum observations of each columns 
- Example of rock data shown below
```{r}
summary(rock)
```

## Criteria
**Satisfied the following Criteria**

1) It must be done in Slidify or Rstudio Presenter
2) It must be 5 pages
3) It must be hosted on github or Rpubs
4) It must contained some embedded R code that gets run when slidifying the document


## Thank You
- Thank you **my parents** for giving birth to me 
- Also, thanks my siblings, **Seaweed & Jaybird**
- Interactive plot of dataset, Rock is below 

```{r, warning=FALSE, message=FALSE}
library(plotly)
library(ggplot2)
library(RColorBrewer)
plot_ly(rock, x= rock$area, y= rock$peri, color = as.factor(rock$perm))
```

